# Example mcmc fitting for Clara

Load important packages

```{r}

library(tidyverse)
#install.packages("BayesianTools") # install if needed
library(BayesianTools)

# Help with plotting posteriors
library(posterior)
library(bayesplot)


```

Simulate the data. 

```{r}

# Imagine this is an exposure rate, which is at 1 for 20 days then switches to 0.5 for 20 days.
sim_data <- c(rep(1, 20), rep(0.5, 20))

# Add noise to estimates (like reporting error)
sim_data_noise <- sim_data + rnorm(40, 0, 0.2)
df_data <- data.frame(
    day = 1:40,
    exp = sim_data_noise
)

# Plot the exposure rate in time with noise:
df_data %>%   
    ggplot() + 
        geom_point(aes(x = day, y = exp))

```

Imagine a situation where we know at day 21 the exposure changes (maybe due to lockdown?) but we don't know to what value. 
We have the simulated data in df_data, but looking at the plot it's not obvious what the exposure changes to.
We can recover our simulated value using a mcmc model!
To do this we will use package called BayesianTools:

```{r}

# likleihood function. 
likelihood1 <- function(param){
    exp_scale <- param[1]
    noise_sd <- param[2]
    likelihoods_pre = dnorm(df_data$exp[1:20], mean = 1, sd = noise_sd, log = T)
    likelihoods_post = dnorm(df_data$exp[21:40], mean = 1 * exp_scale, sd = noise_sd, log = T)

    return(sum(likelihoods_pre, likelihoods_post))  
}

# This function creares the Bayesian model. Under the hood it's creating uniform priors between 0 and 1 for exp_scale and noise_sd.
setUp1 <- createBayesianSetup(likelihood1, lower = c(0, 0), upper = c(1, 1))

# Run for 10,000 steps.
settings = list(iterations = 10000, message = FALSE)
out1 <- runMCMC(bayesianSetup = setUp1, sampler = "Metropolis", settings = settings)

```

Plot the posterior samples

```{r}

posterior <- getSample(out1)

summary(out1)
plot(out1) # plot internally calls tracePlot(out)


```